Using traffic analysis to identify The Second Generation Onion Router

### 2011-04-26 thesis/thesis.tex
Underscores in notes and in refkeys changed

Providing resistance to blocking or censorship comes in many forms. The People's
Republic of China operates a sophisticated Internet firewall capable of blocking
requests to forbidden information \parencite{The-OpenNet-Initiative:2009uq}.
This system is often referred to as the Great Firewall of China. Resisting this
system can involve ignoring spurious reset packets injected into the stream of
forbidden communications \parencite{springerlink:10.1007/11957454_2}, or be as
simple as accessing data through an encrypted proxy as is done in FreeGate
\parencite{Smart:2008kx}.

More sophisticated circumvention tend to be based on anonymity providing
designs, \textcite{Kopsell:2004:ABR:1029179.1029197} describes a censorship
resistant system built on top of AN.ON
\parencite{springerlink:10.1007/3-540-44702-4_7}. Publishing systems such as
Freedom \parencite{Goldberg:1999p2231} and Freenet \parencite{Clarke:2001p2435}
aim to provide censorship resistance as well as anonymity. Infranet uses
steganography to hide sensitive messages in innocuous content Infranet
\parencite{Feamster:2002p307}.

>>>>

Providing resistance to blocking or censorship comes in many forms. The People's
Republic of China operates a sophisticated Internet firewall capable of blocking
requests to forbidden information \parencite{The-OpenNet-Initiative:2009uq}.
This system is often referred to as the Great Firewall of China. Resisting this
system can involve ignoring spurious reset packets injected into the stream of
forbidden communications \parencite{springerlink:10.1007/11957454-2}, or be as
simple as accessing data through an encrypted proxy as is done in FreeGate
\parencite{Smart:2008kx}.

More sophisticated circumvention tend to be based on anonymity providing
designs, \textcite{Kopsell:2004:ABR:1029179.1029197} describes a censorship
resistant system built on top of AN.ON
\parencite{springerlink:10.1007/3-540-44702-4-7}. Publishing systems such as
Freedom \parencite{Goldberg:1999p2231} and Freenet \parencite{Clarke:2001p2435}
aim to provide censorship resistance as well as anonymity. Infranet uses
steganography to hide sensitive messages in innocuous content Infranet
\parencite{Feamster:2002p307}.
